\begin{thebibliography}{999}

\bibitem{r1}
Lahme, S.Z.; Klein, P.; Lehtinen, A.; M\"uller, A.; Pirinen, P.; Ron\v{c}evi\'c, L.; Su\v{s}ac, A.
Physics lab courses under digital transformation: A trinational survey among university lab instructors about the role of new digital technologies and learning objectives.
\textit{Phys. Rev. Phys. Educ. Res.} \textbf{2023}, \textit{19}, 020159.
\href{https://doi.org/10.1103/PhysRevPhysEducRes.19.020159}{https://doi.org/10.1103/PhysRevPhysEducRes.19.020159}.

\bibitem{r2}
Viswanadh, K.S.; Gureja, A.; Walchatwar, N.; Agrawal, R.; Sinha, S.; Chaudhari, S.; Vaidhyanathan, K.; Hussain, A.M.
Engineering End-to-End Remote Labs Using IoT-Based Retrofitting.
\textit{IEEE Access} \textbf{2024}, \textit{PP}, 1--1.
\href{https://doi.org/10.1109/ACCESS.2024.3523066}{https://doi.org/10.1109/ACCESS.2024.3523066}.

\bibitem{r3}
Fuertes, J.J.; Mart\'inez, J.M.; Dormido, S.; Vargas, H.; S\'anchez, J.; Duro, N.
Virtual and Remote Laboratory of a DC Motor for Learning Control Theory.
\textit{Int. J. Eng. Educ.} \textbf{2011}, \textit{27}, 1--12.

\bibitem{r4}
Guerrero-Osuna, H.A.; Garc\'ia-V\'azquez, F.A.; Ibarra-Delgado, S.; Sol\'is-S\'anchez, L.O.
Developing a Cloud and IoT-Integrated Remote Laboratory to Enhance Education 4.0: An Approach for FPGA-Based Motor Control.
\textit{Appl. Sci.} \textbf{2024}, \textit{14}, 10115.

\bibitem{r5}
Lustig, F.; Kuri\v{s}\v{c}\'ak, P.; Brom, P.; Dvo\v{r}\'ak, J.
Open Modular Hardware and Software Kit for Creations of Remote Experiments Accessible from PC and Mobile Devices.
\textit{Int. J. Online Eng. (iJOE)} \textbf{2016}, \textit{12}, 30--36.
\href{https://doi.org/10.3991/ijoe.v12i07.5833}{https://doi.org/10.3991/ijoe.v12i07.5833}.

\bibitem{r6}
Zhao, Y.
Smartphone-Based Undergraduate Physics Labs: A Comprehensive Review.
\textit{IEEE Access} \textbf{2024}, \textit{13}, 1106--1132.
\href{https://doi.org/10.1109/ACCESS.2024.3523066}{https://doi.org/10.1109/ACCESS.2024.3523066}.

\bibitem{r7}
Dizdarevic, J.; Jukan, A.
Engineering an IoT--Edge--Cloud Computing System Architecture: Lessons Learnt from an Undergraduate Laboratory Course.
\textit{IoT} \textbf{2022}, \textit{3}, 145--163.
\href{https://doi.org/10.3390/iot3010010}{https://doi.org/10.3390/iot3010010}.

\bibitem{r8}
Azad, A.K.M.
Use of Internet of Things for Remote Laboratory Settings.
\textit{IoT} \textbf{2021}, \textit{2}, 203--232.
\href{https://doi.org/10.3390/iot2020011}{https://doi.org/10.3390/iot2020011}.

\bibitem{r9}
Palmer, C.; Roullier, B.; Aamir, M.; McQuade, F.; Stella, L.; Anjum, A.
Digital Twinning Remote Laboratories for Online Practical Learning.
\textit{Sensors} \textbf{2022}, \textit{22}, 2351.
\href{https://doi.org/10.3390/s22062351}{https://doi.org/10.3390/s22062351}.

\bibitem{r10}
Lustig, A.; Biard, V. \textit{et al.}
Engineering End-to-End Remote Labs using IoT-based Retrofitting.
\textit{arXiv} \textbf{2024}, arXiv:2402.05466.
Available online: \url{https://arxiv.org/abs/2402.05466} (accessed on 5 December 2025).

\bibitem{r11}
P\'erez-Cham\'e, J.H. \textit{et al.}
Development of an educational low-cost and ESP32-based platform for fundamental physics experiments.
\textit{Comput. Appl. Eng. Educ.} \textbf{2023}.
\href{https://doi.org/10.1002/cae.22674}{https://doi.org/10.1002/cae.22674}.

\bibitem{r12}
Marosan, A. \textit{et al.}
Real-time data acquisition with ESP32 for IoT applications in educational environments.
\textit{Int. Conf. Appl. Math. Sci. (ICMAS)} \textbf{2024}, \textit{19}(2), 61--68.
Available online: \url{http://www.icmas.eu/Journal_archive_files/Vol_19-Issue2_2024_PDF/61-68_MAROSAN.pdf} (accessed on 5 December 2025).

\bibitem{r13}
Idoyaga, I. \textit{et al.}
The Use of Remote Laboratories in University Physics: Challenges and Opportunities in Latin America.
In \textit{Proceedings of the Symposium ICASE-MIDEC GIREP 2023}.
Available online: \url{https://indico.cern.ch/event/1175859/} (accessed on 5 December 2025).

\bibitem{r14}
Vera, M. \textit{et al.}
An\'alisis comparativo de la ense\~nanza de la f\'isica en universidades latinoamericanas durante la pandemia COVID-19.
\textit{Rev. Invecom} \textbf{2025}.
Available online: \url{https://revistainvecom.org/index.php/invecom/article/view/4234} (accessed on 5 December 2025).

\bibitem{r15}
Sosa Mej\'ia, W.S.
\textit{RemotePhysicsLab: Prototipo de laboratorio de f\'isica h\'ibrido basado en IoT}.
Repositorio GitHub.
Available online: \url{https://github.com/waltersosa/RemotePhysicsLab.git} (accessed on 5 December 2025).

\bibitem{r16}
Hevner, A.R.; March, S.T.; Park, J.; Ram, S.
Design Science in Information Systems Research.
\textit{MIS Q.} \textbf{2004}, \textit{28}, 75--105.

\bibitem{r17}
ISO/IEC.
\textit{ISO/IEC 15288:2015 Systems and Software Engineering---System Life Cycle Processes};
International Organization for Standardization: Geneva, Switzerland, 2015.

\bibitem{r18}
Mattel, Inc.
\textit{Hot Wheels Track Sets}.
Available online: \url{https://shop.mattel.com/pages/hot-wheels} (accessed on 5 December 2025).

\bibitem{r19}
Mattel, Inc.
\textit{Hot Wheels Cars}.
Available online: \url{https://shop.mattel.com/collections/hot-wheels-cars} (accessed on 5 December 2025).

\bibitem{r20}
Vishay Intertechnology, Inc.
\textit{TCRT5000 Reflective Optical Sensor}.
Available online: \url{https://www.vishay.com/docs/83751/tcrt5000.pdf} (accessed on 5 December 2025).

\bibitem{r21}
Espressif Systems.
\textit{ESP32-WROOM-32 Datasheet}.
Available online: \url{https://www.espressif.com/sites/default/files/documentation/esp32-wroom-32_datasheet_en.pdf} (accessed on 5 December 2025).

\bibitem{r22}
Thingiverse.
\textit{Mechanical Support for Track-Based Experiments} (Thing 3630616).
Available online: \url{https://www.thingiverse.com/thing:3630616} (accessed on 5 December 2025).

\bibitem{r23}
Thingiverse.
\textit{3D Printed Modular Track Components} (Thing 3485484).
Available online: \url{https://www.thingiverse.com/thing:3485484} (accessed on 5 December 2025).

\bibitem{r24}
Thingiverse.
\textit{3D Printed Structural Reinforcement Parts} (Thing 4381935).
Available online: \url{https://www.thingiverse.com/thing:4381935} (accessed on 5 December 2025).

\bibitem{r25}
Thingiverse.
\textit{3D Printed Mechanical Pusher Mechanism} (Thing 2806324).
Available online: \url{https://www.thingiverse.com/thing:2806324} (accessed on 5 December 2025).

\bibitem{r26}
Tower Pro.
\textit{SG90 Micro Servo Motor Datasheet}.
Available online: \url{http://www.ee.ic.ac.uk/pjs99/projects/servo/sg90_datasheet.pdf} (accessed on 5 December 2025).

\bibitem{r27}
Stepperonline.
\textit{NEMA 17 Stepper Motor Bipolar Datasheet}.
Available online: \url{https://www.omc-stepperonline.com/download/17HS19-2004S1.pdf} (accessed on 5 December 2025).

\bibitem{r28}
STMicroelectronics.
\textit{L298N Dual H-Bridge Motor Driver Datasheet}.
Available online: \url{https://www.st.com/resource/en/datasheet/l298.pdf} (accessed on 5 December 2025).

\bibitem{r29}
Generic Electronics Suppliers.
\textit{LCD 20x4 Display with I2C Interface Datasheet}.
Available online: \url{https://www.sparkfun.com/datasheets/LCD/HD44780.pdf} (accessed on 5 December 2025).

\bibitem{r30}
Generic Electronics Suppliers.
\textit{Tactile Push Button Switch for Breadboard}.
Available online: \url{https://www.adafruit.com/product/367} (accessed on 5 December 2025).

\bibitem{r31}
USB Implementers Forum.
\textit{USB Type-C Cable Specification}.
Available online: \url{https://www.usb.org/sites/default/files/USB\%20Type-C\%20Spec\%20R2.0\%20-\%20August\%202019.pdf} (accessed on 5 December 2025).

\bibitem{r32}
IEEE.
\textit{IEEE Standard for Wireless LAN Medium Access Control (MAC) and Physical Layer (PHY) Specifications}.
Available online: \url{https://ieeexplore.ieee.org/document/9363693} (accessed on 5 December 2025).

\bibitem{r33}
Generic Electronics Suppliers.
\textit{Dupont Jumper Wires (Male-Female and Female-Female)}.
Available online: \url{https://www.adafruit.com/category/289} (accessed on 5 December 2025).

\bibitem{r34}
Generic Electronics Suppliers.
\textit{Plastic Project Enclosure Box (135x75x40 mm)}.
Available online: \url{https://www.digikey.com/en/products/filter/enclosures/287} (accessed on 5 December 2025).

\bibitem{r35}
Generic Electronics Suppliers.
\textit{AC-DC Power Adapter 12V/1A}.
Available online: \url{https://www.digikey.com/en/products/filter/power-supplies-external-internal-off-board/171} (accessed on 5 December 2025).

\bibitem{r36}
Insta360.
\textit{Insta360 Link---4K AI Webcam Technical Specifications}.
Available online: \url{https://onlinemanual.insta360.com/link/en-us/introduction} (accessed on 5 December 2025).

\bibitem{r37}
Raspberry Pi Ltd.
\textit{Raspberry Pi 4 Model B Product Brief}.
Available online: \url{https://datasheets.raspberrypi.com/rpi4/raspberry-pi-4-product-brief.pdf} (accessed on 5 December 2025).

\bibitem{r38}
EMQ Technologies Co., Ltd.
\textit{EMQX---MQTT Platform for IoT Data Streaming Documentation}.
Available online: \url{https://docs.emqx.com/en/emqx/v5.0/} (accessed on 5 December 2025).

\bibitem{r39}
EMQ Technologies Co., Ltd.
\textit{MQTTX: Your All-in-One MQTT Client Toolbox Documentation}.
Available online: \url{https://mqttx.app/docs} (accessed on 5 December 2025).

\bibitem{r40}
OpenJS Foundation.
\textit{Node.js API Documentation}.
Available online: \url{https://nodejs.org/api/} (accessed on 5 December 2025).

\bibitem{r41}
OpenJS Foundation.
\textit{Express API Reference}.
Available online: \url{https://expressjs.com/en/4x/api.html} (accessed on 5 December 2025).

\bibitem{r42}
MongoDB, Inc.
\textit{MongoDB Documentation}.
Available online: \url{https://www.mongodb.com/docs/manual/} (accessed on 5 December 2025).

\bibitem{r43}
Mongoose.
\textit{Mongoose ODM API Documentation}.
Available online: \url{https://mongoosejs.com/docs/api.html} (accessed on 5 December 2025).

\bibitem{r44}
Vercel, Inc.
\textit{Next.js Documentation}.
Available online: \url{https://nextjs.org/docs} (accessed on 5 December 2025).

\bibitem{r45}
Meta Platforms, Inc.
\textit{React Reference Documentation}.
Available online: \url{https://react.dev/reference/react} (accessed on 5 December 2025).

\bibitem{r46}
Arduino AG.
\textit{Arduino IDE 2.x Documentation}.
Available online: \url{https://www.arduino.cc/en/software} (accessed on 5 December 2025).

\bibitem{r47}
Python Software Foundation.
\textit{Python 3 Documentation}.
Available online: \url{https://docs.python.org/3/} (accessed on 5 December 2025).

\bibitem{r48}
Atzori, L.; Iera, A.; Morabito, G.
The Internet of Things: A survey.
\textit{Comput. Netw.} \textbf{2010}, \textit{54}, 2787--2805.
\href{https://doi.org/10.1016/j.comnet.2010.05.010}{https://doi.org/10.1016/j.comnet.2010.05.010}.

\bibitem{r49}
Eraser Labs, Inc.
\textit{Eraser---AI Co-Pilot for Technical Design and Documentation}.
Available online: \url{https://www.eraser.io} (accessed on 5 December 2025).

\bibitem{r50}
OpenAI. \textit{ChatGPT}.
Available online: \url{https://chat.openai.com} (accessed on 23 January 2026). Content generated with the assistance of ChatGPT.

\bibitem{r51}
Hern\'andez, R. \textit{et al.}
Remote Laboratory for developing IoT systems in engineering education.
In \textit{Proceedings of the ACM Technical Symposium on Computer Science Education}; ACM: New York, NY, USA, \textbf{2025}.
\href{https://doi.org/10.1145/3716554.3716602}{https://doi.org/10.1145/3716554.3716602}.

\bibitem{r52}
Chang, H.Y. \textit{et al.}
Deploying an IoT-based remote physics lab platform to support undergraduate mechanics education.
\textit{Phys. Educ.} \textbf{2024}, \textit{59}, 065012.

\bibitem{r53}
Kaur, G. \textit{et al.}
Design and Implementation of ESP32-Based IoT Devices for Real-Time Monitoring Applications.
\textit{Sensors} \textbf{2023}, \textit{23}, 6437.
\href{https://doi.org/10.3390/s23156437}{https://doi.org/10.3390/s23156437}.

\end{thebibliography}
